Backscatter Modulation Design for Symbiotic Radio Networks

### 2021-12-18 main.tex
:pencil: Add optimality proof

		\begin{subsection}{Input probability distribution}
			For any fixed decision boundary $\boldsymbol{t}$ and transmit precoder $\boldsymbol{w}$, the equivalent discrete memoryless \gls{mac} can be determined by \eqref{eq:mac} and problem~\eqref{op:rate_region} boils down to
			\begin{maxi!}
				{\scriptstyle{\boldsymbol{P}}}{I(c_{\mathcal{K}};\boldsymbol{y},z)}{\label{op:input_probability_distribution}}{}
				\addConstraint{\eqref{co:sum_probability},\eqref{co:nonnegative_probability},}
			\end{maxi!}
			which is non-convex for $K > 1$ due to the product term $\prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$. Fortunately, the \gls{kkt} conditions are necessary and sufficient for this type of problem, and the proof follows straightforwardly from \cite{Watanabe2009}.\footnote{For any elementary discrete memoryless \gls{mac} (sizes of input alphabets are no greater than that of output alphabet), the sufficiency can be proved by combining the local maximum and connectedness of \gls{kkt} solutions. For any general discrete memoryless \gls{mac}, the capacity can be achieved by an elementary discrete memoryless \gls{mac} included within. Thus, we restrict the discussion of this paper to elementary discrete memoryless \gls{mac}s.}
			\begin{proposition}
				The necessary and sufficient conditions for an input probability distribution $\boldsymbol{P}^{\star}$ to maximize the weighted sum primary-backscatter rate are that, $\forall m_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$,
				\begin{subequations}
					\begin{alignat}{2}
						I_k(\bar{c}_{m_k};\boldsymbol{y},z) & = I(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_k^{\star}(\bar{c}_{m_k}) > 0,\label{co:probable_states}\\
						I_k(\bar{c}_{m_k};\boldsymbol{y},z) & \le I(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_k^{\star}(\bar{c}_{m_k}) = 0.\label{co:dropped_states}
					\end{alignat}
				\end{subequations}

				\eqref{co:probable_states} means each probable state of each tag should produce the same marginal information (averaged over all states of other tags), while \eqref{co:dropped_states} implies any state of any tag with potentially less marginal information than above should not be used.
				\label{pr:optimal_conditions}
			\end{proposition}
			\begin{proof}
				Denote the Lagrange multiplier associated with \eqref{co:sum_probability} and \eqref{co:nonnegative_probability} as $\boldsymbol{\mu} \triangleq [\mu_1,\ldots,\mu_K]^T \in \mathbb{R}^{K \times 1}$ and $\boldsymbol{\Lambda} \triangleq [\boldsymbol{\lambda}_1^T,\ldots,\boldsymbol{\lambda}_K^T]^T \in \mathbb{R}^{M \times K}$ with $\boldsymbol{\lambda}_k \triangleq [\lambda_{k,1},\ldots,\lambda_{k,M}]^T \in \mathbb{R}^{M \times 1}$, respectively. The Lagrangian function of problem~\eqref{op:input_probability_distribution} is
				\begin{align}
					L(\boldsymbol{P},\boldsymbol{\mu},\boldsymbol{\Lambda})
					& = - I(c_{\mathcal{K}};\boldsymbol{y},z) + \sum_{k \in \mathcal{K}} \mu_k \left( \sum_{m_k \in \mathcal{M}} P_k(\bar{c}_{m_k}) - 1 \right)\nonumber\\
					& \quad - \sum_{k \in \mathcal{K}} \sum_{m_k \in \mathcal{M}} \lambda_{k,m_k} P_k(\bar{c}_{m_k}),
				\end{align}
				and the corresponding \gls{kkt} conditions on the primal and dual solutions are, $\forall m_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$,
				\begin{subequations}
					\begin{equation}
						- \nabla_{P_k^{\star}(\bar{c}_{m_k})} I(c_{\mathcal{K}};\boldsymbol{y},z) + \mu_k^{\star} - \lambda_{k,m_k}^{\star} = 0,
					\end{equation}
					\begin{equation}
						\lambda_{k,m_k}^{\star} = 0, \quad P_k^{\star}(\bar{c}_{m_k}) > 0,
					\end{equation}
					\begin{equation}
						\lambda_{k,m_k}^{\star} \ge 0, \quad P_k^{\star}(\bar{c}_{m_k}) = 0,
					\end{equation}
				\end{subequations}
				where the directional derivative can be explicitly expressed as
				\begin{equation}
					\nabla_{P_k^{\star}(\bar{c}_{m_k})} I(c_{\mathcal{K}};\boldsymbol{y},z) = I_k(\bar{c}_{m_k};\boldsymbol{y},z) - (1 - \rho).
				\end{equation}

				Due to the necessity and sufficiency of the \gls{kkt} conditions, we conclude that any input probability distribution $\boldsymbol{P}^{\star}$ maximizes the weighted sum primary-backscatter rate if and only if, $\forall m_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$,
				\begin{subequations}
					\begin{alignat}{2}
						I_k(\bar{c}_{m_k};\boldsymbol{y},z) & = \mu_k^{\star} + (1 - \rho), \quad && P_k^{\star}(\bar{c}_{m_k}) > 0,\\
						I_k(\bar{c}_{m_k};\boldsymbol{y},z) & \le \mu_k^{\star} + (1 - \rho), \quad && P_k^{\star}(\bar{c}_{m_k}) = 0,
					\end{alignat}
				\end{subequations}
				which implies
				\begin{equation}
					\sum_{m_k} P_k^{\star}(\bar{c}_{m_k}) I_k(\bar{c}_{m_k};\boldsymbol{y},z) = \mu_k^{\star} + (1 - \rho).
				\end{equation}

@@

			\begin{theorem}
				The input probability distribution that achieves the weighted sum primary-backscatter capacity, at state $m_k \in \mathcal{M}$ of tag $k \in \mathcal{K}$, is given by the converging point of sequence\footnote{Note that the probability distribution of tag $k$ is based on the updated probability distribution of tags $1,\ldots,k-1$.}
				\begin{equation}
					P_k^{(r+1)}(\bar{c}_{m_k}) = \frac{P_k^{(r)}(\bar{c}_{m_k}) \exp \left( \frac{\rho}{1 - \rho} I_k(\bar{c}_{m_k};\boldsymbol{y},z) \right)}{\sum_{m_k'} P_k^{(r)}(\bar{c}_{m_k'}) \exp \left( \frac{\rho}{1 - \rho} I_k(\bar{c}_{m_k'};\boldsymbol{y},z) \right)},
					\label{eq:optimal_distribution}
				\end{equation}
				where $r \in \mathbb{Z}_+$ is the iteration index and $P_k^{(0)}(\bar{c}_{m_k}) > 0$, $\forall m_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$.
				\label{th:optimal_distribution}
			\end{theorem}
			\begin{proof}
				We first prove sequence~\eqref{eq:optimal_distribution} is non-decreasing in mutual information. For state $m_k \in \mathcal{M}$ of tag $k \in \mathcal{K}$, let $P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) = \prod_{q \in \mathcal{K}} P_q(\bar{c}_{m_q})$ and $P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) = P_k'(\bar{c}_{m_k}) \prod_{q \in \mathcal{K} \setminus \{k\}} P_q(\bar{c}_{m_q})$ be two probability distributions with potentially different marginal for tag $k$, and denote the corresponding mutual information and received energy distribution as $I(\bar{c}_{\mathcal{K}};\boldsymbol{y},z)$, $I'(\bar{c}_{\mathcal{K}};\boldsymbol{y},z)$ and $P(\bar{z}_j)$, $P'(\bar{z}_j)$, respectively. Also, define an intermediate function $J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right)$ by \eqref{eq:intermediate_information_function}. Apparently, $I(\bar{c}_{\mathcal{K}};\boldsymbol{y},z) = J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) \right)$.
				\begin{figure*}[!b]
					\hrule
					\begin{align}
						J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right)
						& \triangleq \rho \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right)\nonumber\\
						& \quad + (1 - \rho) \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}})}{P'(\bar{z}_j) P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}})}.
						\label{eq:intermediate_information_function}
					\end{align}
				\end{figure*}
				For a fixed $P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}})$, $J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right)$ is a concave function of $P_k(\bar{c}_{m_k})$ and is maximized at $\nabla_{P_k^{\star}(\bar{c}_{m_k})} J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right) = 0$, namely
				\begin{equation}
					S_k'(\bar{c}_{m_k}) - S_k'(\bar{c}_{i_k}) + (1 - \rho) \log \frac{P_k(\bar{c}_{i_k})}{P_k^{\star}(\bar{c}_{m_k})} = 0,
					\label{eq:optimal_intermediate_information_condition}
				\end{equation}
				where $i_k \ne m_k$ is the reference state and
				\begin{align}
					S_k'(\bar{c}_{m_k})
					& \triangleq I_k(\bar{c}_{m_k};\boldsymbol{y},z) + (1 - \rho) \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}})\nonumber\\
					& \quad \times \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K} \setminus \{k\}}},\bar{c}_{m_k}) \log P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}},\bar{c}_{m_k}).
				\end{align}

@@

				On the other hand, choosing $P_k(\bar{c}_{m_k})$ by \eqref{eq:optimal_relative_distribution} also satisfies
				\begin{subequations}
					\label{eq:information_difference_upper}
					\begin{align}
						\Delta
						& \triangleq I(\bar{c}_{\mathcal{K}};\boldsymbol{y},z) - J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right)\\
						& = (1 - \rho) \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P'(\bar{z}_j) P_k(\bar{c}_{m_k})}{P(\bar{z}_j) P_k'(\bar{c}_{m_k})}\\
						& = (1 - \rho) \sum_{m_k} \frac{P_k'(\bar{c}_{m_k}) u_k(\bar{c}_{m_k})}{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) u_k(\bar{c}_{m_k'})} \sum_j P(\bar{z}_j \mid \bar{c}_{m_k})\nonumber\\
						& \quad \times \log \frac{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) P(\bar{z}_j \mid \bar{c}_{m_k'}) u_k(\bar{c}_{m_k})}{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) P(\bar{z}_j \mid \bar{c}_{m_k'}) u_k(\bar{c}_{m_k'})}\\
						& \ge (1 - \rho) \sum_{m_k} \frac{P_k'(\bar{c}_{m_k}) u_k(\bar{c}_{m_k})}{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) u_k(\bar{c}_{m_k'})} \sum_j P(\bar{z}_j \mid \bar{c}_{m_k})\nonumber\\
						& \quad \times \left( 1 - \frac{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) P(\bar{z}_j \mid \bar{c}_{m_k'}) u_k(\bar{c}_{m_k'})}{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) P(\bar{z}_j \mid \bar{c}_{m_k'}) u_k(\bar{c}_{m_k})} \right)\\
						& = 0,
					\end{align}
				\end{subequations}
				where $u_k(\bar{c}_{m_k}) \triangleq \exp \left( \frac{\rho}{1 - \rho} I_k(\bar{c}_{m_k};\boldsymbol{y},z) \right)$ and the equality holds if and only if \eqref{eq:optimal_relative_distribution} converges. Combining \eqref{eq:information_difference_lower} and \eqref{eq:information_difference_upper} suggests $I(\bar{c}_{\mathcal{K}};\boldsymbol{y},z) \ge I'(\bar{c}_{\mathcal{K}};\boldsymbol{y},z)$. Since mutual information is bounded above, we conclude sequence \eqref{eq:optimal_distribution} is convergent and non-decreasing in mutual information.
			\end{proof}
		\end{subsection}

>>>>

		\begin{subsection}{Input probability distribution}
			For any fixed decision boundary $\boldsymbol{t}$ and transmit precoder $\boldsymbol{w}$, the equivalent discrete memoryless \gls{mac} can be determined by \eqref{eq:mac} and problem~\eqref{op:rate_region} boils down to
			\begin{maxi!}
				{\scriptstyle{\boldsymbol{P}}}{I(c_{\mathcal{K}};\boldsymbol{y},z)}{\label{op:input_probability_distribution}}{}
				\addConstraint{\eqref{co:sum_probability},\eqref{co:nonnegative_probability},}
			\end{maxi!}
			which is non-convex for $K > 1$ due to the product term $\prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$. Fortunately, the \gls{kkt} conditions are necessary and sufficient for this type of problem, and the proof follows straightforwardly from \cite{Watanabe2009}.\footnote{For any elementary discrete memoryless \gls{mac} (sizes of input alphabets are no greater than that of output alphabet), the sufficiency can be proved by combining the local maximum and connectedness of \gls{kkt} solutions. For any general discrete memoryless \gls{mac}, the capacity can be achieved by an elementary discrete memoryless \gls{mac} included within. Thus, we restrict the discussion of this paper to elementary discrete memoryless \gls{mac}s.}
			\begin{proposition}
				The necessary and sufficient conditions for an input probability distribution $\boldsymbol{P}^{\star}$ to maximize the weighted sum primary-backscatter rate are that, $\forall m_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$,
				\begin{subequations}
					\label{eq:optimal_conditions}
					\begin{alignat}{2}
						I_k(\bar{c}_{m_k};\boldsymbol{y},z) & = I(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_k^{\star}(\bar{c}_{m_k}) > 0,\label{eq:probable_states}\\
						I_k(\bar{c}_{m_k};\boldsymbol{y},z) & \le I(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_k^{\star}(\bar{c}_{m_k}) = 0.\label{eq:dropped_states}
					\end{alignat}
				\end{subequations}
				\eqref{eq:probable_states} means each probable state of each tag should produce the same marginal information (averaged over all states of other tags), while \eqref{eq:dropped_states} implies any state of any tag with potentially less marginal information than above should not be used.
				\label{pr:optimal_conditions}
			\end{proposition}
			\begin{proof}
				Denote the Lagrange multiplier associated with \eqref{co:sum_probability} and \eqref{co:nonnegative_probability} as $\boldsymbol{\mu} \triangleq [\mu_1,\ldots,\mu_K]^T \in \mathbb{R}^{K \times 1}$ and $\boldsymbol{\Lambda} \triangleq [\boldsymbol{\lambda}_1^T,\ldots,\boldsymbol{\lambda}_K^T]^T \in \mathbb{R}^{M \times K}$ with $\boldsymbol{\lambda}_k \triangleq [\lambda_{k,1},\ldots,\lambda_{k,M}]^T \in \mathbb{R}^{M \times 1}$, respectively. The Lagrangian function of problem~\eqref{op:input_probability_distribution} is
				\begin{align}
					L(\boldsymbol{P},\boldsymbol{\mu},\boldsymbol{\Lambda})
					& = - I(c_{\mathcal{K}};\boldsymbol{y},z) + \sum_{k \in \mathcal{K}} \mu_k \left( \sum_{m_k \in \mathcal{M}} P_k(\bar{c}_{m_k}) - 1 \right)\nonumber\\
					& \quad - \sum_{k \in \mathcal{K}} \sum_{m_k \in \mathcal{M}} \lambda_{k,m_k} P_k(\bar{c}_{m_k}),
				\end{align}
				and the corresponding \gls{kkt} conditions on the primal and dual solutions are, $\forall m_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$,
				\begin{subequations}
						- \nabla_{P_k^{\star}(\bar{c}_{m_k})} I(c_{\mathcal{K}};\boldsymbol{y},z) + \mu_k^{\star} - \lambda_{k,m_k}^{\star} = 0,
						\lambda_{k,m_k}^{\star} = 0, \quad P_k^{\star}(\bar{c}_{m_k}) > 0,
						\lambda_{k,m_k}^{\star} \ge 0, \quad P_k^{\star}(\bar{c}_{m_k}) = 0,
				\end{subequations}
				where the directional derivative can be explicitly expressed as
					\nabla_{P_k^{\star}(\bar{c}_{m_k})} I(c_{\mathcal{K}};\boldsymbol{y},z) = I_k(\bar{c}_{m_k};\boldsymbol{y},z) - (1 - \rho).

				Due to the necessity and sufficiency of the \gls{kkt} conditions, we conclude that any input probability distribution $\boldsymbol{P}^{\star}$ maximizes the weighted sum primary-backscatter rate if and only if, $\forall m_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$,
				\begin{subequations}
					\begin{alignat}{2}
						I_k(\bar{c}_{m_k};\boldsymbol{y},z) & = \mu_k^{\star} + (1 - \rho), \quad && P_k^{\star}(\bar{c}_{m_k}) > 0,\label{eq:probable_states_marginal}\\
						I_k(\bar{c}_{m_k};\boldsymbol{y},z) & \le \mu_k^{\star} + (1 - \rho), \quad && P_k^{\star}(\bar{c}_{m_k}) = 0,\label{eq:dropped_states_marginal}
					\end{alignat}
				\end{subequations}
				which implies
				\begin{equation}
					\sum_{m_k} P_k^{\star}(\bar{c}_{m_k}) I_k(\bar{c}_{m_k};\boldsymbol{y},z) = \mu_k^{\star} + (1 - \rho).
				\end{equation}

@@

			\begin{theorem}
				The input probability distribution that achieves the weighted sum primary-backscatter capacity, at state $m_k \in \mathcal{M}$ of tag $k \in \mathcal{K}$, is given by the converging point of sequence\footnote{Note that the probability distribution of tag $k$ is based on the updated probability distribution of tags $1,\ldots,k-1$.}
				\begin{equation}
					P_k^{(r+1)}(\bar{c}_{m_k}) = \frac{P_k^{(r)}(\bar{c}_{m_k}) \exp \left( \frac{\rho}{1 - \rho} I_k(\bar{c}_{m_k};\boldsymbol{y},z) \right)}{\sum_{m_k'} P_k^{(r)}(\bar{c}_{m_k'}) \exp \left( \frac{\rho}{1 - \rho} I_k(\bar{c}_{m_k'};\boldsymbol{y},z) \right)},
					\label{eq:optimal_distribution}
				\end{equation}
				where $r \in \mathbb{Z}_+$ is the iteration index and $P_k^{(0)}(\bar{c}_{m_k}) > 0$.
				% , $\forall m_k \in \mathcal{M}$ and $\forall k \in \mathcal{K}$.
				\label{th:optimal_distribution}
			\end{theorem}
			\begin{proof}
				We first prove sequence~\eqref{eq:optimal_distribution} is non-decreasing in mutual information. For state $m_k \in \mathcal{M}$ of tag $k \in \mathcal{K}$, let $P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) = \prod_{q \in \mathcal{K}} P_q(\bar{c}_{m_q})$ and $P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) = P_k'(\bar{c}_{m_k}) \prod_{q \in \mathcal{K} \setminus \{k\}} P_q(\bar{c}_{m_q})$ be two probability distributions with potentially different marginal for tag $k$, and denote the corresponding mutual information and received energy distribution as $I(\bar{c}_{\mathcal{K}};\boldsymbol{y},z)$, $I'(\bar{c}_{\mathcal{K}};\boldsymbol{y},z)$ and $P(\bar{z}_j)$, $P'(\bar{z}_j)$, respectively. Also, define an intermediate function $J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right)$ by \eqref{eq:intermediate_information_function}. Apparently, $I(\bar{c}_{\mathcal{K}};\boldsymbol{y},z) = J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) \right)$.
				\begin{figure*}[!b]
					\hrule
					\begin{align}
						J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right)
						& \triangleq \rho \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right)\nonumber\\
						& \quad + (1 - \rho) \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}})}{P'(\bar{z}_j) P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}})}.
						\label{eq:intermediate_information_function}
					\end{align}
				\end{figure*}
				For a fixed $P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}})$, $J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right)$ is a concave function of $P_k(\bar{c}_{m_k})$ and is maximized at $\nabla_{P_k^{\star}(\bar{c}_{m_k})} J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right) = 0$, namely
				\begin{equation}
					S_k'(\bar{c}_{m_k}) - S_k'(\bar{c}_{i_k}) + (1 - \rho) \log \frac{P_k(\bar{c}_{i_k})}{P_k^{\star}(\bar{c}_{m_k})} = 0,
					\label{eq:optimal_intermediate_information_condition}
				\end{equation}
				where $i_k \ne m_k$ is the reference state and
				\begin{align}
					S_k'(\bar{c}_{m_k})
					& \triangleq I_k(\bar{c}_{m_k};\boldsymbol{y},z) + (1 - \rho) \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}})\nonumber\\
					& \quad \times \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K} \setminus \{k\}}},\bar{c}_{m_k}) \log P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}},\bar{c}_{m_k}).
				\end{align}

@@

				On the other hand, choosing $P_k(\bar{c}_{m_k})$ by \eqref{eq:optimal_relative_distribution} also satisfies
				\begin{subequations}
					\label{eq:information_difference_upper}
					\begin{align}
						\Delta
						& \triangleq I(\bar{c}_{\mathcal{K}};\boldsymbol{y},z) - J \left( P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}),P_{\mathcal{K}}'(\bar{c}_{m_{\mathcal{K}}}) \right)\\
						& = (1 - \rho) \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P'(\bar{z}_j) P_k(\bar{c}_{m_k})}{P(\bar{z}_j) P_k'(\bar{c}_{m_k})}\\
						& = (1 - \rho) \sum_{m_k} \frac{P_k'(\bar{c}_{m_k}) u_k(\bar{c}_{m_k})}{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) u_k(\bar{c}_{m_k'})} \sum_j P(\bar{z}_j \mid \bar{c}_{m_k})\nonumber\\
						& \quad \times \log \frac{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) P(\bar{z}_j \mid \bar{c}_{m_k'}) u_k(\bar{c}_{m_k})}{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) P(\bar{z}_j \mid \bar{c}_{m_k'}) u_k(\bar{c}_{m_k'})}\\
						& \ge (1 - \rho) \sum_{m_k} \frac{P_k'(\bar{c}_{m_k}) u_k(\bar{c}_{m_k})}{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) u_k(\bar{c}_{m_k'})} \sum_j P(\bar{z}_j \mid \bar{c}_{m_k})\nonumber\\
						& \quad \times \left( 1 - \frac{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) P(\bar{z}_j \mid \bar{c}_{m_k'}) u_k(\bar{c}_{m_k'})}{\sum_{m_k'} P_k'(\bar{c}_{m_k'}) P(\bar{z}_j \mid \bar{c}_{m_k'}) u_k(\bar{c}_{m_k})} \right)\\
						& = 0,
					\end{align}
				\end{subequations}
				where $u_k(\bar{c}_{m_k}) \triangleq \exp \left( \frac{\rho}{1 - \rho} I_k(\bar{c}_{m_k};\boldsymbol{y},z) \right)$ and the equality holds if and only if \eqref{eq:optimal_relative_distribution} converges. Combining \eqref{eq:information_difference_lower} and \eqref{eq:information_difference_upper} suggests $I(\bar{c}_{\mathcal{K}};\boldsymbol{y},z) \ge I'(\bar{c}_{\mathcal{K}};\boldsymbol{y},z)$. Since mutual information is bounded above, we conclude sequence \eqref{eq:optimal_distribution} is non-decreasing and convergent in mutual information.

				We then prove any converging point of sequence \eqref{eq:optimal_distribution}, denoted as $P_k^{\star}(\bar{c}_{m_k})$, fulfills the optimal conditions \eqref{eq:optimal_conditions} and achieves the weighted primary-backscatter sum capacity. To see this, define
				\begin{equation}
					D_k^{(r)}(\bar{c}_{m_k}) \triangleq \frac{P_k^{(r+1)}(\bar{c}_{m_k})}{P_k^{(r)}(\bar{c}_{m_k})} = \frac{u_k(\bar{c}_{m_k})}{\sum_{m_k'} P_k^{(r)}(\bar{c}_{m_k'}) u_k(\bar{c}_{m_k'})},
				\end{equation}
				where $P_k^{(0)}(\bar{c}_{m_k}) > 0$. As sequence \eqref{eq:optimal_distribution} is convergent, any state with $P_k^{\star}(\bar{c}_{m_k}) > 0$ need to satisfy $D_k^{\star}(\bar{c}_{m_k}) \triangleq \lim_{r \to \infty} D_k^{(r)}(\bar{c}_{m_k}) = 1$, namely
				\begin{equation}
					I_k(\bar{c}_{m_k};\boldsymbol{y},z) = \frac{1 - \rho}{\rho} \log \sum_{m_k'} P_k^{(r)}(\bar{c}_{m_k'}) u_k(\bar{c}_{m_k'}),
				\end{equation}
				which coincides with \eqref{eq:probable_states_marginal} and implies \eqref{eq:probable_states}. That is, given $P_k^{(0)}(\bar{c}_{m_k}) > 0$, any converging point with $P_k^{\star}(\bar{c}_{m_k}) > 0$ must satisfy \eqref{eq:probable_states}.
				On the other hand, we assume $P_k^{\star}(\bar{c}_{m_k})$ does not satisfy \eqref{eq:dropped_states}, such that for any state with $P_k^{\star}(\bar{c}_{m_k}) = 0$,
				% On the other hand, we show if $P_k^{\star}(\bar{c}_{m_k})$ does not satisfy \eqref{eq:dropped_states}, then it is not a converging point of sequence \eqref{eq:optimal_distribution}. By this assumption, for any state with $P_k^{\star}(\bar{c}_{m_k}) = 0$,
				\begin{equation}
					I_k(\bar{c}_{m_k};\boldsymbol{y},z) > I(c_{\mathcal{K}};\boldsymbol{y},z) = \sum_{m_k'} P_k^{\star}(\bar{c}_{m_k'}) I_k(\bar{c}_{m_k'};\boldsymbol{y},z),
				\end{equation}
				where the equality origins from \eqref{eq:backscatter_sum_rate_expectation} and \eqref{eq:primary_ergodic_rate_expectation}. Since the exponential function is monotonically increasing, we have $u_k(\bar{c}_{m_k}) > \sum_{m_k'} P_k^{\star}(\bar{c}_{m_k'}) u_k(\bar{c}_{m_k'})$ and $D_k^{\star}(\bar{c}_{m_k}) > 1$. Considering $P_k^{(0)}(\bar{c}_{m_k}) > 0$ and $P_k^{\star}(\bar{c}_{m_k}) = 0$, it contradicts with
				\begin{equation}
					P_k^{(r)}(\bar{c}_{m_k}) = P_k^{(0)}(\bar{c}_{m_k}) \prod_{n=1}^r D_k^{(n)}(\bar{c}_{m_k}).
				\end{equation}
				Therefore, given $P_k^{(0)}(\bar{c}_{m_k}) > 0$, any converging point with $P_k^{\star}(\bar{c}_{m_k}) = 0$ must satisfy \eqref{eq:dropped_states}.

				In conclusion, sequence \eqref{eq:optimal_distribution} always converges to a weighted sum capacity-achieving distribution for state $m_k$ of tag $k$.
			\end{proof}
		\end{subsection}
